### 2018-04-05 pubs/itp-2018/sections/proof-reconstruction.tex
[ ref.bib ] Add the master thesis reference to introduce uh function.
Added a mention to the master thesis to skip all the proofs.

@@

The remainder of this section will be devoted to present a formal
description in type theory of remaining \Metis rules presented in
Table~\ref{tab:agda-metis-table} using the pattern presented in the
example above. We follow the same order to present the rules as the
table shows.

>>>>

We skip all the proofs in the following sections to keep the length of
this document. Nevertheless, these proofs and other intermediate
results are presented in~\cite{Prieto-Cubides2017a}. We remind the
reader the formalisation~\cite{AgdaMetis,AgdaProp} contains also these
proofs type-checked by \Agda.

@@

The remainder of this section will be devoted to present a formal
description in type theory of the remaining \Metis rules presented in
Table~\ref{tab:agda-metis-table} using the pattern presented in the
example above. We follow the same order to present the rules as the
table shows.

### 2018-04-05 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ ref.bib ] Add the master thesis reference to introduce uh function.
Added a mention to the master thesis to skip all the proofs.

Unluckily, \Metis does not make explicit in the \TSTP derivation
the way it uses the subgoals to prove the goal. We show that way
in the correctness of the \strip inference rule in Theorem~\ref{thm:strip}.
To show that, we first need to prove Lemma~\ref{lem:inv-uh-lem} and
Lemma~\ref{lem:lem-inv-strip}.

\begin{mainlemma}
  \label{lem:inv-uh-lem}
Let $\text{n} : \Nat$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where

\begin{equation}
\label{eq:uh-structured}
\begin{aligned}
&\hspace{.495mm} \fuh_{1} : \Prop → \Nat → \Prop\\
&\begin{array}{llll}
\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
\fuh_{1} &φ &n &= φ.
\end{array}
\end{aligned}
\end{equation}
\end{mainlemma}

To keep simpler the coming definitions, we use instead of $\fuh_{1}$ function
a unary function defined in~\eqref{eq:uh}.

\begin{align*}
  \label{eq:uh}
  \begin{split}
  &\fuh : \Prop → \Prop\\
  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
  \end{split}
\end{align*}
Using the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.

>>>>

Unluckily, \Metis does not make explicit in the \TSTP derivation
the way it uses the subgoals to prove the goal. We show that way
in the correctness of the \strip inference rule in Theorem~\ref{thm:strip}.
To show that, we first need to state Lemma~\ref{lem:inv-uh-lem} and
Lemma~\ref{lem:lem-inv-strip}.

\begin{mainlemma}
  \label{lem:inv-uh-lem}
If $Γ ⊢ \fuh~φ$ then $Γ ⊢ φ$ where
\begin{align}
  \label{eq:uh}
  \begin{split}
  &\fuh : \Prop → \Prop\\
  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
  \end{split}
\end{align}
\end{mainlemma}

In~\cite{Prieto-Cubides2017a}, we make a complete treatment for
terminating functions including the analysis of the function $\fuh$
showed in~\eqref{eq:uh}. The goal of this function comes from the
defintion of $\fuh_{1}$ function in~\eqref{eq:uh-structured}. It consists of
contracting a formula $φ₁ ⇒ (φ₂ ⇒ φ₃)$ to $(φ₁ ∧ φ₂) ⇒ φ₃$, and expanding a
formula $φ₁ ⇒ (φ₂ ∧ φ₃)$ to $(φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$.

\begin{equation}
\label{eq:uh-structured}
\begin{aligned}
&\hspace{.495mm} \fuh_{1} : \Prop → \Nat → \Prop\\
&\begin{array}{llll}
\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
\fuh_{1} &φ &n &= φ.
\end{array}
\end{aligned}
\end{equation}
The remining function is $\fuh_{cm}$. This functions outputs the complexity
measure for the $\fuh_{1}$ function (see more details in Section 2.1
in~\cite{Prieto-Cubides2017a}).
